Analysis of the properties of probabilistic models in learning problems with an expert

### 2022-01-30 paper/Grabovoy2022ExpertLearningAIT/Manuscript.tex
fix ait

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto .   
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.}
}
\subtitle{}

\titlerunning{Probabilistic models in learning with an expert}        % if too long for running head

\author{Andrey V. Grabovoy        \and
            Alexandra I. Bazarova  \and
            Vadim V. Strijov
}

%\authorrunning{Short form of author list} % if too long for running head
\institute{
            Andrey V. Grabovoy\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{grabovoy.av@phystech.edu}
           \and
           Alexandra I. Bazarova\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{bazarova.ai@phystech.edu}
           \and
           Vadim V. Strijov \at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{strijov@phystech.edu}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
This paper is devoted to the construction of interpretable models in machine learning. 
It solves the problem of approximating a given set of figures on a contour image.
Assumptions are introduced that the figures are curves of the second order.
When approximating figures, information about the type, location and form of curves, as well as the set of their possible transformations, is used.
Such information is called \textit{expert}, and the machine learning method based on expert information is called \textit {expert learning}.
It is assumed that the set of shapes is approximated by a set of \textit {local models}.
Each local model, based on expert information, approximates one shape in the contour image.
To build models, it is proposed to map second-order curves into a feature space where each local model is a linear model.
Thus, higher-order curves are recognized using the composition of linear models.
As an applied problem, the problem of approximating the iris of the eye on a contour image is considered.
\keywords{Mixture of experts \and Expert learning \and Linear models \and Interpretabe models}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{real_image}\label{intro:fig1:real}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{outline_image}\label{intro:fig1:outer}} 
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences}
\label{intro:fig1}
\end{figure}

@@

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{900.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{901.eps}}
	\subfloat[]{\includegraphics[height = 0.2\textheight]{902.eps}}

@@

\begin{figure}[h]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{900noise.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{901noise.eps}}\\
	\subfloat[]{\includegraphics[height = 0.2\textheight]{902noise.eps}}

\caption{Dependence of the parameters  $r$, $x_0$ and $y_0$ on the iteration number for different prior distributions. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig4}
\end{figure}

@@

\subsection{Iris approximations }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.17\textheight]{not_prior_real_example}} 
	\subfloat[]{\includegraphics[height = 0.17\textheight]{prior_real_example}}
	\subfloat[]{\includegraphics[height = 0.17\textheight]{prior_regular_real_example}} 
\caption{Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified}
\label{ce:fig6}
\end{figure}

@@

\section{Acknowledgments}
\label{sec:7}
The reported study was funded by RFBR according to the research projects 20-37-90050, 19-07-01155 and NTI project 13/1251/2018.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{Akhtar2018}
Akhtar N, Mian A (2018) Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey. IEEE Access 6:14410--14430

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Sample document for preparing papers to  "Avtomatika i Telemekhanika"
%%  charset=utf-8
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{a&t}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{bm}
\usepackage{url}
\usepackage{multirow}
\renewcommand{\baselinestretch}{2}
\usepackage{cmap}
\usepackage{autonum}
\usepackage{cite}

\usepackage[labelformat=empty]{caption}

\begin{document}  %%%!!!

\year{2022}

\title{Analysis of the properties of probabilistic models in learning problems with an expert}%
\thanks{The reported study was funded by Russian Foundation for Basic Research according to the research projects 20-37-90050, 19-07-01155 and National Technological Initiative project 13/1251/2018.}

\authors{А.В.~ГРАБОВОЙ (grabovoy.av@phystech.edu)\\
(Московский физико-технический институт),\\
В.В.~СТРИЖОВ, д-р~физ.-мат.~наук (strijov@phystech.edu)\\
(Вычислительный центр им. А.А. Дородницына ФИЦ ИУ РАН)}

@@

\begin{abstract}
This paper is devoted to the construction of interpretable models in machine learning. 
It solves the problem of approximating a given set of figures on a contour image.
Assumptions are introduced that the figures are curves of the second order.
When approximating figures, information about the type, location and form of curves, as well as the set of their possible transformations, is used.
Such information is called \textit{expert}, and the machine learning method based on expert information is called \textit {expert learning}.
It is assumed that the set of shapes is approximated by a set of \textit {local models}.
Each local model, based on expert information, approximates one shape in the contour image.
To build models, it is proposed to map second-order curves into a feature space where each local model is a linear model.
Thus, higher-order curves are recognized using the composition of linear models.
As an applied problem, the problem of approximating the iris of the eye on a contour image is considered.

\smallskip\\
\textit{Ключевые слова}: Mixture of experts; Expert learning;  Linear models; Interpretabe models.
\end{abstract}

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{real_image}\label{intro:fig1:real}
\includegraphics[width=0.5\textwidth]{outline_image}\label{intro:fig1:outer}
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences}
\label{intro:fig1}
\end{figure}

@@

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
	\includegraphics[height = 0.2\textheight]{900.eps}
	\includegraphics[height = 0.2\textheight]{901.eps}
	\includegraphics[height = 0.2\textheight]{902.eps}

@@

\begin{figure}[h]
	\includegraphics[height = 0.2\textheight]{900noise.eps}
	\includegraphics[height = 0.2\textheight]{901noise.eps}
	\includegraphics[height = 0.2\textheight]{902noise.eps}
\caption{Dependence of the parameters  $r$, $x_0$ and $y_0$ on the iteration number for different prior distributions. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig4}
\end{figure}

@@

\subsection{Iris approximations }
\begin{figure}[h!]
	\includegraphics[height = 0.17\textheight]{not_prior_real_example}
	\includegraphics[height = 0.17\textheight]{prior_real_example}
	\includegraphics[height = 0.17\textheight]{prior_regular_real_example}
\caption{Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified}
\label{ce:fig6}
\end{figure}

@@

\begin{thebibliography}{}
\bibitem{Akhtar2018}
Akhtar N, Mian A (2018) Threat of Adversarial Attacks on Deep Learning in Computer Vision: A Survey. IEEE Access 6:14410--14430
